Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-14 paper/paper.qmd

```{r}

Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

>>>>

Data from Study 1 were used to show the relative amount of belief in free will of the average Taiwanese real estate agents and how much are they satisfied with their job across two times within 6 months with the same sample.
We extracted the responses from the survey and extracted the responses to the questions : "From the scale of 0 to 10, How much do you agree with this statement: I have free will"and "From the scale of 0 to 10, How much do you agree with this statement: I am satisfied with my job" at Time one and two.
In Figure 1, we calculated and showed the means and standard deviation of the job satisfaction both times and belief in free will values.

```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)
